Mesh Refinement and Derefinement of Two-Moment Radiation Fields

### 2020-11-10 Documents/M1/MeshRefinement/MeshRefinement.tex
Added curvilinear coordinates to MeshRefinement documentation

>>>>

\section{Curvilinear Coordinates}

\subsection{Preliminaries}

The introduction of curvilinear coordinates doesn't change any of the preliminaries.

\subsection{Refinement}

The refinement
section does change, in that when demanding equality of the cell averages, the metric determinant
must be taken into account, i.e., Eq.~\eqref{eq:refinementProjection} becomes
\begin{equation}
  \int_{\vect{k}_{(j)}}u_{h}^{(j)}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
  =\int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x},\quad i=1,\ldots,M.
  \label{eq:refinementProjection_CC}
\end{equation}
Evaluating the left-hand side of Eq.~\eqref{eq:refinementProjection_CC} gives
\begin{equation}
  \int_{\vect{k}_{(j)}}u_{h}^{(j)}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
  =|\vect{k}_{(j)}|\,w_{i}\,u_{i}^{(j)}\,\sqrt{\gamma_{i}}.
  \end{equation}
  Evaluating the right-hand side of Eq.~\eqref{eq:refinementProjection_CC} gives
  \sd{Why isn't this integrated over $\vect{\xi}$?}
  \footnote{I found  $\int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
  =|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\xi})\,\ell_{k}(\vect{\eta}(\vect{\xi}))\,\sqrt{\gamma}\,d\vect{\xi}\,U_{k}$}
  \begin{equation}
  \int_{\vect{k}_{(j)}}U_{h}(\vect{x})\,\ell_{i}^{(j)}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
  =|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\eta})\,\ell_{k}(\vect{\xi}(\vect{\eta}))\,\sqrt{\gamma}\,d\vect{\eta}\,U_{k}.
\end{equation}
Defining the projection matrix, $P^{\left(j\right)}_{\gamma}$, with components
\begin{equation}
P^{\left(j\right)}_{ik,\gamma}
=\int_{\vect{i}_{(j)}}\ell_{i}^{(j)}(\vect{\eta})\,\ell_{k}(\vect{\xi}(\vect{\eta}))\,\sqrt{\gamma}\,d\vect{\eta},
\end{equation}
and the diagonal matrix $\mathcal{D}_{\gamma}
=\mbox{diag}(\sqrt{\gamma_{1}}\,w_{1},\ldots,\sqrt{\gamma_{M}}\,w_{M})$, the components of the expansion in the refined element $\vect{k}_{(j)}$ are obtained from the matrix-vector product
\begin{equation}
  \mathcal{D}_{\gamma}\,\vect{u}^{(j)} = \mathcal{P}^{(j)}_{\gamma}\,\vect{U}.
\end{equation}
Since $\gamma=\gamma\left(t\right)$, $\mathcal{P}^{\left(j\right)}_{\gamma}$ and $\cD_{\gamma}$
must be computed at each time step.

\subsection{Coarsening}

As with refinement, Eq.~\eqref{eq:coarseningProjection} becomes
\begin{equation}
  \int_{\vect{K}}U_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
  =\int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}.
  \label{eq:coarseningProjection_CC}
\end{equation}
Evaluating the left-hand side of Eq.~\eqref{eq:coarseningProjection_CC} gives
\begin{equation}
  \int_{\vect{K}}U_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
  =|\vect{K}|\,w_{i}\,U_{i}\,\sqrt{\gamma_{i}}.
\end{equation}
Evaluating the right-hand side of Eq.~\eqref{eq:coarseningProjection_CC} gives
  \sd{Why isn't this integrated over $\vect{\xi}$?}
\footnote{I found $\int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
  =\sum_{j=1}^{N}|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}(\vect{\eta}(\vect{\xi}))\,\ell_{k}^{\left(j\right)}(\vect{\xi})\,\sqrt{\gamma}\,d\vect{\xi}\,u_{k}^{(j)}$}
\begin{equation}
  \int_{\vect{K}}u_{h}(\vect{x})\,\ell_{i}(\vect{x})\,\sqrt{\gamma}\,d\vect{x}
  =\sum_{j=1}^{N}|\vect{k}_{(j)}|\sum_{k=1}^{M}\int_{\vect{i}_{(j)}}\ell_{i}(\vect{\xi}(\vect{\eta}))\,\ell_{k}(\vect{\eta})\,\sqrt{\gamma}\,d\vect{\eta}\,u_{k}^{(j)}.
\end{equation}
Thus,
\begin{equation}
  \mathcal{D}_{\gamma}\,\vect{U}=\sum_{j=1}^{N}\f{|\vect{k}_{(j)}|}{|\vect{K}|}
  \big(\mathcal{P}_{\gamma}^{(j)}\big)^{\trans}\,\vect{u}^{(j)}.
\end{equation}
For a refinement factor of $2$, $|\vect{k}_{(j)}|/|\vect{K}|=2^{-d}$.

\subsection{Mapping $\eta\rightarrow\xi$}
For a 1D problem with two subcells, the mapping from the coarse reference element, coordinatized
by $\eta$, to the fine reference element, coordinatized by $\xi$, is
\begin{equation}
\xi\left(\eta\right)=\frac{1}{2}\left(\eta+\frac{1}{2}\left(-1\right)^{k}\right),\hspace{1em}k=1,2.
\end{equation}
